A note on observation processes in epidemic models

### 2019-07-31 ms/ms.tex
minor tweaks

\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
\usepackage[top=1in,left=1in, right = 1in, footskip=1in]{geometry}

@@

Differences in the direction of the bias can be explained by the estimates of the
exponential growth rate ($r = \beta - \gamma$) and the mean infectious period ($1/\gamma$).
In general, we expect delays in observation processes to make the observed epidemic 
time series last longer and have smaller peaks (Figure 1).
When we fit the recovery model to an infection time series, the model overestimates
the initial growth rate in order to match the bigger (and faster) epidemic peak of the 
infection time series. When the mean infectious period is fixed, higher growth rate
translates to higher basic reproduction number as we see in Figure 2B. When we allow
the mean infectious period to vary, the model still over estimates the growth rate but
also underestimates the mean infectious period (high $\gamma$), 
which decreases the overall estimate of the basic reproduction number.
Likewise, fitting the infection model to a recovery time series underestimates
the growth rate to match the smaller (and slower) epidemic peak; this 
underestimates the basic reproduction number when the mean infectious period is fixed. 
When we allow the mean infectious period to vary, we overestimate the mean infectious
period, which in turn increaseses the estimate of the basic reproduction number.

>>>>

\documentclass[12pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
\usepackage[top=1in,left=1in, right = 1in, footskip=1in]{geometry}

@@

Differences in the direction of the bias can be explained by the estimates of the
exponential growth rate ($r = \beta - \gamma$) and the mean infectious period ($1/\gamma$).
In general, we expect delays in observation processes to make the observed epidemic 
time series last longer and have smaller peaks (Figure 1).
When we fit the recovery model to an infection time series, the model overestimates
the initial growth rate in order to match the bigger (and faster) epidemic peak of the 
infection time series. When the mean infectious period is fixed, higher growth rate
translates to higher basic reproduction number as we see in Figure 2B. When we allow
the mean infectious period to vary, the model still over estimates the growth rate but
also underestimates the mean infectious period (high $\gamma$), 
which decreases the overall estimate of the basic reproduction number.
Likewise, fitting the infection model to a recovery time series underestimates
the growth rate to match the smaller (and slower) epidemic peak; this 
underestimates the basic reproduction number when the mean infectious period is fixed. 
When we allow the mean infectious period to vary, we overestimate the mean infectious
period, which in turn increases the estimate of the basic reproduction number.
